### 2018-09-14 ICRA19/intro.tex
Added Haoran's images
reviewed the intro and related work, added info on experiments.
updated the first 2 images

 \begin{figure}
\centering
\renewcommand{\figwid}{\columnwidth}
\begin{overpic}[width =\figwid]{firstpic.pdf}%\put(1,55){a)}
\end{overpic}
\caption{\label{fig:leadfigure} 
     Reshaping particles by collisions with rigid bodies. Top pictures illustrates using closed boundaries to reshape the particles. Bottom pictures illustrates angle of repose of different particles.
}
\end{figure}

>>>>

 \begin{figure}
\centering
\renewcommand{\figwid}{\columnwidth}
\begin{overpic}[width =\figwid]{firstpic.pdf}%\put(1,55){a)}
\end{overpic}
\vspace{-2em}
\caption{\label{fig:leadfigure} 
     Reshaping particles by collisions with rigid bodies. Top pictures illustrate using closed boundaries to reshape the particles. 
      Bottom pictures illustrate with different particles how varying the the angle of attack modifies the shape of particles remaining on a rigid object and how modifying the applied force changes the angle of repose.
}
\vspace{-1em}
\end{figure}
